A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-02-24 manuscript.Rmd
add (R) Markdown, Git as header for cross references

```{r schematic, eval = TRUE, echo = FALSE, fig.cap="Schematic illustration of the interplay of the four components (in dashed boxes) central to the reproducible workflow: version control (Git), dependency management (Make), software management (Docker), and dynamic document generation (R Markdown). Git tracks changes to the project over time. Make manages dependencies among the files. Docker provides a container in which the final report is built using dynamic document generation in R Markdown. Reproduced from @Peikert2019.  "}
# file gets downloaded in Makefile
knitr::include_graphics("images/nutshell.svg", auto_pdf = TRUE)
```

@@

@@

We will later see how this simplicity enables us to create many different document formats (i.e. Word, PDF, HTML) and incorporate code (i.e. R, Python, Julia).
Another advantage of Markdown is that you can easily version-control it with Git.
You may be familiar with Microsoft Words' "Track Changes"-Feature and version control is similar in its basic idea but more potent in its features.
Instead of tracking only one file, you can keep track of the whole project directory, and instead of losing all changes when you agree to them, the entire history is preserved transparently.
For example, this paper has been going through `r length(git2r::commits())` `r link("https://github.com/aaronpeikert/repro-tutorial/commits/master", "iterations")`.
To activate Git in a given project, you can call:
<!-- Hands-on: Introduce Git -->

@@

>>>>

```{r schematic, eval = TRUE, echo = FALSE, fig.cap="Schematic illustration of the interplay of the four components (in dashed boxes) central to the reproducible workflow: version control (Git), dependency tracking (Make), software management (Docker), and dynamic document generation (R Markdown). Git tracks changes to the project over time. Make manages dependencies among the files. Docker provides a container in which the final report is built using dynamic document generation in R Markdown. Reproduced from @Peikert2019.  "}
# file gets downloaded in Makefile
knitr::include_graphics("images/nutshell.svg", auto_pdf = TRUE)
```

@@

## Markdown

@@

We will later see how this simplicity enables us to create many different document formats (i.e. Word, PDF, HTML) and incorporate code (i.e. R, Python, Julia).

## Git

Another advantage of Markdown is that you can easily version-control it with Git.
You may be familiar with Microsoft Words' "Track Changes"-Feature and version control is similar in its basic idea but more potent in its features.
Instead of tracking only one file, you can keep track of the whole project directory, and instead of losing all changes when you agree to them, the entire history is preserved transparently.
For example, this paper has been going through `r length(git2r::commits())` `r link("https://github.com/aaronpeikert/repro-tutorial/commits/master", "iterations")`.
To activate Git in a given project, you can call:
<!-- Hands-on: Introduce Git -->

@@

### R Markdown
